Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

In Section 3 we will concentrate on centrality and activity in evolving social
network. We will define what centrality or activity is good, and we will design
some instance of those metrics by the standard we set. In Section 4, we will
give the algorithms to compute our designed centrality and activity from the
online data structure which maintains the evolving social network. We will also
show how to quickly locate significant vertices that has high activity or
centrality at a specific time. In Section 5, we will show the metrics make
sense with real world data.

@@

In Section 2 we will discuss the known properties of a typical social network,
which could be helpful for our algorithm designs. In Section 4, we will
establish a framework of data structure and algorithms to solve series of
possible queries including computing the metrics about a evolving social
network.

@@

\subsection{Definition}
\definition A \textbf{pure growing model} for an evolving graph $EG$ is defined
in pair \begin{equation}
EG=(V,E),
\end{equation}
where $V$ is the set of all nodes in the network, and $E$
is the set of edges, formally an edge $e\in E$ for $e=(u,v,t)$,
where $u,v\in V$ are the two end points of the edge, $u<v$ (to ensure
bidirectional), $t\in \mathbb{N}$. The $t$ component stored the forming time of
the graph. As for weighted evolving graph model, we modifies $e\in E$ for
$e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands for the multiplicity of the
edge, which might be useful in some circumstances, and the others stay the same
meaning. In the unweighted case, we can simply set $w=1$ for all edges.

\definition The historical edge set $E_t$
\begin{equation}
E_t=\{e\;|\;e(u,v,t',w)\in E\text{ and }t'\leq t\}.
\end{equation}
An immediate statement one can ensure is
\begin{equation}
\forall t, E_t\subseteq E\text{ and }p\leq q\implies E_p\subseteq E_q.
\end{equation}

Define $G_t$ to be the graph formed by $V$ and $E_t$. So $G_t$ is the snapshot
of the whole network at time $t$.

Now we define the update of an evolving graph in our model. First we assume all
possible active vertices has been already defined, so $V$ does not change.
\definition 
$EG^*=(V,E^*)$ where $E\subseteq E^*$. We assume the edges are added to the
model by correct time order, so
\begin{equation}
\forall e\in E^*\setminus E, \forall e'\in E, e=(u,v,t,w)\text{ and }
e'=(u',v',t',w'), t\geq t'.
\end{equation}

And we define the notation of some frequently used basic functions:

\definition The adjacency matrix.
\begin{equation}
A(G_t)=\begin{pmatrix}a_{ij}\end{pmatrix}_{n\times n},\text{ where }n=|V|,
a_{ij}\in \mathbb{R}^+,
\end{equation}
is the adjacency matrix of the graph at time $t$. More detailed
\begin{equation}
a_{ij}=\begin{cases}
0&(i=j)\\
\sum_{e\in E_t\text{ and }e=(i,j,t,w)}w &(i<j)\\
a_{ji}&(i>j)
\end{cases}
\end{equation}

@@

\subsection{Properties}
In most social networks, people have their own friendship circles, and the
average circle size is quite limited because people do less interaction with
strangers than their close friends or family members. We call this phenomenon
the \textbf{sparsity} of social network.
\definition Reduced edge set (historical) $E_t^\bullet=\{(x_i,y_i)\}$:
\begin{equation}
(x,y)\in E_t^\bullet \iff \exists e(x,y,t,w)\in E_t.
\end{equation}
\definition Reduced degree $k^\bullet(G_t,v)$:
\begin{equation}
k^\bullet(G_t,v)=\#\{u\;|\;(u,v)\in E_t^\bullet\text{ or }(v,u)\in
E_t^\bullet\}.
\end{equation}

@@

We want the metrics to derive other functions, so it will be nice if we can
limit the range of the function.
\begin{equation}
0\leq \mathit{Act}(G_t,v) \leq 1.
\end{equation}

@@

A node with no neighbors is totally inactive.
\begin{equation}
k(G_t,v)=0\implies \mathit{Act}(G_t,v)=0.
\end{equation}
Also we declare
\begin{equation}
k(G_{-\infty},v)=0.
\end{equation}

@@

If a vertex $v$ performs an interaction $(v,u)$ at time $t$, i.e., a new edge
is added to $G_t$, and suppose the interaction is the only change to the graph
at time $t$, then the activity of $v$ should be greater than if the edge is not
added.

\begin{equation}
E_t=E'_t\cup\{e(u,v,t,w)\}\implies \mathit{Act}(G_{t},v)>\mathit{Act}(G'_{t},v
),\label{eq-mono}
\end{equation}

@@

There exists a function $g$, such that for any possible change
$E_{t+1}=E_t\cup\{e_i(u_i,v_i,t+1,w_i)\}|_{i=1}^n$,

\begin{equation}
\mathit{Act}(G_{t+\varepsilon},v)=g(\mathit{Act}(G_t,v),n,\{w_i\},\varepsilon),
\qquad (0<\varepsilon<2)\label{eq-sym}
\end{equation}

@@

Namely, there exists constants $M>0$, such that for any
graph $G_T$ with $T$ as the final updating time, if $k(G_T,v)\neq 0$,
\begin{equation}
\int_{-\infty}^{\infty} \mathit{Act}(G_t,v)\mathrm{d}t/k(G_T,v)\in\left[\frac{1}{M},M\right].
\label{eq-int}
\end{equation}

\definition the \textbf{integral quality} of $\mathit{Act}$ is the minimal such $M$.

@@

@@

\definition $a_{\mu,\eta}(G_t,v)$ is the \textbf{evolving activity} for node $v$, if
\begin{equation}
a(G_t,v)=\begin{cases}
0& (z\geq 0)\\
\mu^{1/z} & (z<0)
\end{cases},
\end{equation}
where $\mu>1$ is the \textbf{decay rate}, and $z$ is a status variable that can
be determined by the following routine:
\begin{itemize}
\item $z=0$ initially, and $z$ can never exceed $0$.
\item $z$ decrease by $\left(\eta\sum_i w_i\right)$, when new edges with weight
$w_i$'s are created by $v$, as discussed in \eqref{eq-sym}, Here $\eta>0$ is the
\textbf{activity delay}.
\item $z$ increase consistently by time, at the same rate of $t$.
\end{itemize}

\begin{theorem}
evolving activity satisfies both normalization and initialization.
\end{theorem}
\begin{proof}
Since the initial value of $z$ is $0$ and $z\leq 0$, by definition we have
$a(G_t,v)=0$ if $v$ is never changed, because there are no chance for $z$
to be less than $0$.

@@

\begin{theorem}
evolving activity satisfies monotonicity.
\end{theorem}
\begin{proof}
Refer to \eqref{eq-mono}, we have $z$ for $G$ at time $t$ is decreased, and
is thus at least $\eta w$ less than $z'$ for $G'$ at time $t$, namely
\begin{equation}z\leq z'-\eta w<0.\end{equation}
If $z'=0$, then
\begin{equation}
a(G'_t,v)=0<a(G_t,v)=\mu^{1/z}.
\end{equation}
Otherwise if $z'<0$,
\begin{equation}
z<z'\implies \mu^{1/z}>\mu^{1/z'},
\end{equation}
hence
\begin{equation}
a(G_t,v)>a(G'_t,v).
\end{equation}
\end{proof}

\begin{theorem}
evolving activity satisfies symmetry.
\end{theorem}
\begin{proof}
Refer to \eqref{eq-sym}, we can write
\begin{equation}
g(a(G_t,v),n,\left\{w_i\right\},\varepsilon)=\begin{cases}
0 &(z^*\geq 0)\\
\mu^{1/z^*}& (z^*=0)
\end{cases},
\end{equation}
where
\begin{equation}
z^*=z+\varepsilon-\eta \sum_i w_i,
\end{equation}
and
\begin{equation}
z=\begin{cases}
0&(a(G_t,v)=0)\\
1/\log_{\mu}a(G_t,v)&(a(G_t,v)>0)
\end{cases}.
\end{equation}
So such $g$ exists.
\end{proof}

\begin{theorem}
evolving activity satisfies locality.
\end{theorem}
\begin{proof}
By definition, $z$ will not be affected by non-local change.
\end{proof}

\begin{theorem}
evolving activity satisfies integrity.
\end{theorem}
\begin{proof}
	%TODO
\end{proof}

\definition \textbf{evolving centrality} $\textbf{x}(G_t)$ is a vector in space
$\mathbb{R}^{|V|}$, where
\begin{equation}
\mathbf{x}=\alpha DA^\bullet \mathbf{x} + \beta\mathbf{1},
\end{equation}
$A^\bullet$ is the 0/1 adjacency matrix of $E^\bullet_t$ as defined in Section 2,
because centrality accentuate more on the structure of the network but not the
intensity of edges. And
$D$ is a diagonal matrix that
\begin{equation}
D_{ij}=\begin{cases}
0&(i\neq j)\\
\mathit{Act}(G_t,v_i)&(i=j)
\end{cases}
\end{equation}
Then $\textbf{x}_i(G_t)$ is the centrality for node $v_i$ in $G_t$, and is
scale-relative to the influence of $v_i$ in the network at time $t$.

@@

\definition \textbf{evolving PageRank} $\textbf{x}(G_t)$ is a vector in space
$\mathbb{R}^{|V|}$, where
\begin{equation}
\mathbf{x}=\alpha DKA \mathbf{x} + \beta\mathbf{1},
\end{equation}
where $A_{ij}$ stands for the total weight of edges from $j$ to $i$,
\begin{equation}
D_{ij}=\begin{cases}
0&(i\neq j)\\
\mathit{Act}(G_t,v_i)&(i=j)
\end{cases};\qquad
K_{ij}=\begin{cases}
0&(i\neq j)\\
k_{\mathrm{out}}(G_t,v_i)&(i=j)
\end{cases}.
\end{equation}

@@

adds $e(v_i,v_j,t,w)$ to the graph and update the graph,
defined in Algorithm \ref{alg-add}.
\item \textsc{Query Degree}($t,v$)

returns $k(G_t,v)$, defined in Algorithm \ref{alg-deg}.
\item \textsc{Query Connectivity}($t,u,v$)

returns whether $u$ and $v$ is connected in the network at time $t$,
defined in
Algorithm \ref{alg-con}.
\item \textsc{Query Activity}($t,v$)

returns the evolving activity $a_{\mu,\eta}(G_t,v)$, defined in
Algorithm \ref{alg-act}.
\item \textsc{Query Centrality}($t$, $\alpha$, $\beta$, $\mathbf{x}_0$, $m$)

returns the active centrality vector $\mathbf{x}(G_t)$. Algorithm
\ref{alg-cen} use the iteration method start with $\mathbf{x}_0$ and for
$m$ times.
\item \textsc{Modify Mu}($\mu'$)

change the value of $\mu$ which defines the evolving activity, in case the
current $\mu$ is inappropriate, defined in algorithm \ref{alg-mu}.
\item \textsc{Modify Eta}($\eta'$)

change the value of $\eta$ which defines the evolving activity, in case the
current $\eta$ is inappropriate, defined in algorithm \ref{alg-eta}.
\end{itemize}

@@

\begin{center} \begin{tikzpicture}[y=.3cm, x=.3cm, font=\sffamily]
 	%axis
	\draw (0,0) -- coordinate (x axis mid) (31, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 19);
	%ticks
	\foreach \x in {2,4,...,30}
		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
	\foreach \y in {2,4,...,18}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	%labels      
	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Queries ($\times10^5$)};
	\node[rotate=90, left=0.8cm] at (0, 12) {\scriptsize Running Time (sec.)};
	%plots
	\draw[color=red!70!black] plot[mark=*, mark options={fill=white}] file {exp-n2w};
	\draw[color=green!50!black] plot[mark=square*, mark options={fill=white}] file {exp-n10w};
	\draw[color=blue!80!black] plot[mark=triangle*, mark options={fill=white}] file {exp-n50w};
	%legend
	\begin{scope}[shift={(2,13)}]
	\draw[color=red!70!black] (0,0) -- plot[mark=*, mark options={fill=white}] (1,0) -- (2,0)
		node[right]{\scriptsize number of nodes=20,000};
	\draw[color=green!50!black] (0,1) -- plot[mark=square*, mark options={fill=white}] (1,1) -- (2,1)
		node[right]{\scriptsize number of nodes=100,000};
	\draw[color=blue!90!black] (0,2) -- plot[mark=triangle*, mark options={fill=white}] (1,2) -- (2,2)
		node[right]{\scriptsize number of nodes=500,000};
	\end{scope}
\end{tikzpicture} \end{center}

@@

>>>>

In section 3 we will concentrate on centrality and activity in evolving social
network. We will define what centrality or activity is good, and we will design
some instance of those metrics by the standard we set. In section 4, we will
give the algorithms to compute our designed centrality and activity from the
online data structure which maintains the evolving social network. We will also
show how to quickly locate significant vertices that has high activity or
centrality at a specific time. In section 5, we will show the metrics make
sense with real world data.

@@

In section 2 we will discuss the known properties of a typical social network,
which could be helpful for our algorithm designs. In section 4, we will
establish a framework of data structure and algorithms to solve series of
possible queries including computing the metrics about a evolving social
network.

@@

\subsection{Definition}
\begin{definition}
A \textbf{pure growing model} for an evolving graph $EG$ is defined in pair:
\begin{equation}
EG=(V,E),
\end{equation}
where $V$ is the set of all nodes in the network, and $E$ is the set of edges,
formally an edge $e\in E$ for $e=(u,v,t)$, where $u,v\in V$ are the two end
points of the edge, $u<v$ (to ensure bidirectional), $t\in \mathbb{N}$. The $t$
component stored the forming time of the graph. As for weighted evolving graph
model, we modifies $e\in E$ for $e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands
for the multiplicity of the edge, which might be useful in some circumstances,
and the others stay the same meaning. In the unweighted case, we can simply set
$w=1$ for all edges.
\end{definition}

\begin{definition}
The historical edge set $E_t$
\begin{equation}
E_t=\{e\;|\;e(u,v,t',w)\in E\text{ and }t'\leq t\}.
\end{equation}
An immediate statement one can ensure is
\begin{equation}
\forall t: E_t\subseteq E\text{ and }p\leq q\implies E_p\subseteq E_q.
\end{equation}

Define $G_t$ to be the graph formed by $V$ and $E_t$. So $G_t$ is the snapshot
of the whole network at time $t$.
\end{definition}

Now we define the update of an evolving graph in our model. First we assume all
possible active vertices has been already defined, so $V$ does not change.

\begin{definition}
$EG^*=(V,E^*)$ where $E\subseteq E^*$. We assume the edges are added to the
model by correct time order, so
\begin{equation}
\forall (u,v,t,w) \in E^*\setminus E,\, \forall (u',v',t',w')\in E: t \geq t'.
\end{equation}
\end{definition}

And we define the notation of some frequently used basic functions:
\begin{definition}
The adjacency matrix
\begin{equation}
A(G_t)=\begin{pmatrix}a_{ij}\end{pmatrix}_{n\times n},\text{ where }n=|V|,
a_{ij}\in \mathbb{R}^+,
\end{equation}
is the adjacency matrix of the graph at time $t$. More detailed
\begin{equation}
a_{ij}=\begin{cases}
0&(i=j)\\
\sum_{e\in E_t\text{ and }e=(i,j,t,w)}w &(i<j)\\
a_{ji}&(i>j)
\end{cases}
\end{equation}
\end{definition}

@@

\subsection{Properties}
In most social networks, people have their own friendship circles, and the
average circle size is quite limited because people do less interaction with
strangers than their close friends or family members. We call this phenomenon
the \textbf{sparsity} of social network.

\begin{definition}
Reduced edge set (historical) $E_t^\bullet=\{(x_i,y_i)\}$:
\begin{equation}
(x,y)\in E_t^\bullet \iff \exists e: e=(x,y,t,w)\in E_t.
\end{equation}
\end{definition}

\begin{definition}
Reduced degree $k^\bullet(G_t,v)$:
\begin{equation}
k^\bullet(G_t,v)=\Big|\{u\;|\;(u,v)\in E_t^\bullet\text{ or }(v,u)\in
E_t^\bullet\}\Big|.
\end{equation}
\end{definition}

@@

We want the metrics to derive other functions, so it will be nice if we can
limit the range of the function:
\begin{equation}
0\leq \mathit{Act}(G_t,v) \leq 1.
\end{equation}

@@

A node with no neighbors is totally inactive:
\begin{equation}
k(G_t,v)=0\implies \mathit{Act}(G_t,v)=0.
\end{equation}
Also we declare that
\begin{equation}
k(G_{-\infty},v)=0.
\end{equation}

@@

If a vertex $v$ performs an interaction $(v,u)$ at time $t$, i.e., a new edge
is added to $G_t$, and suppose the interaction is the only change to the graph
at time $t$, then the activity of $v$ should be greater than if the edge is not
added.
\begin{equation}
E_t=E'_t\cup\{e(u,v,t,w)\}\implies \mathit{Act}(G_{t},v)>\mathit{Act}(G'_{t},v
).\label{eq-mono}
\end{equation}

@@

There exists a function $g$, such that for any possible change
$E_{t+1}=E_t\cup\{e_i(u_i$, $v_i$, $t+1$, $w_i)\}|_{i=1}^n$,

\begin{equation}
\mathit{Act}(G_{t+\varepsilon},v)=g(\mathit{Act}(G_t,v),n,\{w_i\},\varepsilon),
\label{eq-sym}
\end{equation}
where $0<\varepsilon<2$.

@@

Namely, there exists constants $M>0$, such that for any
graph $G_T$ with $T$ as the final updating time, if $k(G_T,v)\neq 0$,
\begin{equation}
\int_{-\infty}^{\infty} \frac{\mathit{Act}(G_t,v)}{k(G_T,v)}\mathrm{d}t\in\left[\frac{1}{M},M\right].
\label{eq-int}
\end{equation}

@@

\begin{definition}
The \textbf{integral quality} of $\mathit{Act}$ is the minimal such $M$.
\end{definition}

@@

\begin{definition}[Evolving Activity]
$a_{\mu,\eta}(G_t,v)$ is the \textbf{evolving activity} for node $v$, if
\begin{equation}
a(G_t,v)=\begin{cases}
0& (z\geq 0)\\
\mu^{1/z} & (z<0)
\end{cases},
\end{equation}
where $\mu>1$ is the \textbf{decay rate}, and $z$ is a status variable that can
be determined by the following routine:
\begin{itemize}
\item $z=0$ initially, and $z$ can never exceed $0$.
\item $z$ decrease by $\left(\eta\sum_i w_i\right)$, when new edges with weight
$w_i$'s are created by $v$, as discussed in \eqref{eq-sym}, Here $\eta>0$ is the
\textbf{activity delay}.
\item $z$ increase consistently by time, at the same rate of $t$.
\end{itemize}
\end{definition}

\begin{theorem}
Evolving activity satisfies both normalization and initialization.
\end{theorem}
\begin{proof}
Since the initial value of $z$ is $0$ and $z\leq 0$, by definition we have
$a(G_t,v)=0$ if $v$ is never changed, because there are no chance for $z$
to be less than $0$.

@@

\begin{theorem}
Evolving activity satisfies monotonicity.
\end{theorem}
\begin{proof}
Refer to \eqref{eq-mono}, we have $z$ for $G$ at time $t$ is decreased, and
is thus at least $\eta w$ less than $z'$ for $G'$ at time $t$, namely
\begin{equation}z\leq z'-\eta w<0.\end{equation}
If $z'=0$, then
\begin{equation}
a(G'_t,v)=0<a(G_t,v)=\mu^{1/z}.
\end{equation}
Otherwise if $z'<0$,
\begin{equation}
z<z'\implies \mu^{1/z}>\mu^{1/z'},
\end{equation}
hence
\begin{equation}
a(G_t,v)>a(G'_t,v).
\end{equation}
\end{proof}

\begin{theorem}
Evolving activity satisfies symmetry.
\end{theorem}
\begin{proof}
Refer to \eqref{eq-sym}, we can write
\begin{equation}
g(a(G_t,v),n,\left\{w_i\right\},\varepsilon)=\begin{cases}
0 &(z^*\geq 0)\\
\mu^{1/z^*}& (z^*=0)
\end{cases},
\end{equation}
where
\begin{equation}
z^*=z+\varepsilon-\eta \sum_i w_i,
\end{equation}
and
\begin{equation}
z=\begin{cases}
0&(a(G_t,v)=0)\\
1/\log_{\mu}a(G_t,v)&(a(G_t,v)>0)
\end{cases}.
\end{equation}
So such $g$ exists.
\end{proof}

\begin{theorem}
Evolving activity satisfies locality.
\end{theorem}
\begin{proof}
By definition, $z$ will not be affected by non-local change.
\end{proof}

\begin{theorem}
Evolving activity satisfies integrity.
\end{theorem}
\begin{proof}
	%TODO
\end{proof}

\begin{definition}[Evolving Centrality]
\textbf{Evolving centrality} $\textbf{x}(G_t)$ is a vector in space
$\mathbb{R}^{|V|}$, where
\begin{equation}
\mathbf{x}=\alpha DA^\bullet \mathbf{x} + \beta\mathbf{1},
\end{equation}
$A^\bullet$ is the 0/1 adjacency matrix of $E^\bullet_t$ as defined in section 2,
because centrality accentuate more on the structure of the network but not the
intensity of edges. And
$D$ is a diagonal matrix that
\begin{equation}
D_{ij}=\begin{cases}
0&(i\neq j)\\
\mathit{Act}(G_t,v_i)&(i=j)
\end{cases}
\end{equation}
Then $\textbf{x}_i(G_t)$ is the centrality for node $v_i$ in $G_t$, and is
scale-relative to the influence of $v_i$ in the network at time $t$.
\end{definition}

@@

\begin{definition}[Evolving PageRank]
\textbf{Evolving PageRank} $\textbf{x}(G_t)$ is a vector in space
$\mathbb{R}^{|V|}$, where
\begin{equation}
\mathbf{x}=\alpha DKA \mathbf{x} + \beta\mathbf{1},
\end{equation}
where $A_{ij}$ stands for the total weight of edges from $j$ to $i$,
\begin{equation}
D_{ij}=\begin{cases}
0&(i\neq j)\\
\mathit{Act}(G_t,v_i)&(i=j)
\end{cases};\qquad
K_{ij}=\begin{cases}
0&(i\neq j)\\
k_{\mathrm{out}}(G_t,v_i)&(i=j)
\end{cases}.
\end{equation}
\end{definition}

@@

Add $e(v_i,v_j,t,w)$ to the graph and update the graph,
defined in algorithm \ref{alg-add}.
\item \textsc{Query Degree}($t,v$)

Return $k(G_t,v)$, defined in algorithm \ref{alg-deg}.
\item \textsc{Query Connectivity}($t,u,v$)

Return whether $u$ and $v$ is connected in the network at time $t$, defined in
algorithm \ref{alg-con}.

\item \textsc{Query Activity}($t,v$)

Returns the evolving activity $a_{\mu,\eta}(G_t,v)$, defined in algorithm
\ref{alg-act}.

\item \textsc{Query Centrality}($t$, $\alpha$, $\beta$, $\mathbf{x}_0$, $m$)

Return the active centrality vector $\mathbf{x}(G_t)$. Algorithm \ref{alg-cen}
use the iteration method start with $\mathbf{x}_0$ and for $m$ times.

\item \textsc{Modify Mu}($\mu'$)

Change the value of $\mu$ which defines the evolving activity, in case the
current $\mu$ is inappropriate, defined in algorithm \ref{alg-mu}.

\item \textsc{Modify Eta}($\eta'$)

Change the value of $\eta$ which defines the evolving activity, in case the
current $\eta$ is inappropriate, defined in algorithm \ref{alg-eta}.
\end{itemize}

@@

\begin{center} \begin{tikzpicture}[y=.3cm, x=.3cm, font=\sffamily]
 	%axis
	\draw (0,0) -- coordinate (x axis mid) (31, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 19);
	%ticks
	\foreach \x in {2,4,...,30}
		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
	\foreach \y in {2,4,...,18}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	%labels      
	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Operations ($\times10^5$)};
	\node[rotate=90, left=0.8cm] at (0, 12) {\scriptsize Running Time (sec.)};
	%plots
	\draw[color=red!70!black] plot[mark=*, mark options={fill=white}] file {exp-n2w};
	\draw[color=green!50!black] plot[mark=square*, mark options={fill=white}] file {exp-n10w};
	\draw[color=blue!80!black] plot[mark=triangle*, mark options={fill=white}] file {exp-n50w};
	%legend
	\begin{scope}[shift={(2,13)}]
	\draw[color=red!70!black] (0,0) -- plot[mark=*, mark options={fill=white}] (1,0) -- (2,0)
		node[right]{\scriptsize number of nodes=20,000};
	\draw[color=green!50!black] (0,1) -- plot[mark=square*, mark options={fill=white}] (1,1) -- (2,1)
		node[right]{\scriptsize number of nodes=100,000};
	\draw[color=blue!90!black] (0,2) -- plot[mark=triangle*, mark options={fill=white}] (1,2) -- (2,2)
		node[right]{\scriptsize number of nodes=500,000};
	\end{scope}
\end{tikzpicture} \end{center}

@@

\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
 	%axis
	\draw (0,0) -- coordinate (x axis mid) (21, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 14);
	%ticks
	\foreach \x in {1,2,...,20}
		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
	\foreach \y in {2,4,...,13}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	%labels      
	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Nodes ($\times10^5$)};
	\node[rotate=90, left=0.8cm] at (0, 12) {\scriptsize Running Time (sec.)};
	%plots
	\draw[color=red!70!black] plot[mark=*, mark options={fill=white}] file {exp-q10w};
	\draw[color=green!50!black] plot[mark=square*, mark options={fill=white}] file {exp-q50w};
	\draw[color=blue!80!black] plot[mark=triangle*, mark options={fill=white}] file {exp-q100w};
	%legend
	\begin{scope}[shift={(2,11)}]
	\draw[color=red!70!black] (0,0) -- plot[mark=*, mark options={fill=white}] (1,0) -- (2,0)
		node[right]{\scriptsize number of Operations=100,000};
	\draw[color=green!50!black] (0,1) -- plot[mark=square*, mark options={fill=white}] (1,1) -- (2,1)
		node[right]{\scriptsize number of Operations=500,000};
	\draw[color=blue!90!black] (0,2) -- plot[mark=triangle*, mark options={fill=white}] (1,2) -- (2,2)
		node[right]{\scriptsize number of Operations=1000,000};
	\end{scope}
\end{tikzpicture} \end{center}
